\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
  {\Huge \scshape Swaroop Patil} \\ \vspace{1pt}
  Pune, Maharashtra \\ \vspace{1pt}
  \small \href{tel:#}{ \raisebox{-0.1\height}\faPhone\ \underline{+91-9172061027} ~} \href{mailto:swarooppatil850@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{swarooppatil850@gmail.com}} ~ 
  \href{https://linkedin.com/in/swarooppatilx}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{Linkedin}}  ~
  \href{https://github.com/swarooppatilx}{\raisebox{-0.2\height}\faGithub\ \underline{Github}} ~
  \href{https://x.com/swarooppatilx}{\raisebox{-0.2\height}\faTwitter\ \underline{Twitter}} ~
  \href{https://swarooppatilx.github.io}{\raisebox{-0.2\height}\faGlobe\ \underline{Website}} ~
\end{center}
\vspace{0.5mm}


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AISSMS Institute of Information Technology, Pune}{2023 – 2027}
      {B.Tech - Information Technology - \textbf{CGPA} - \textbf{9.0}}{Pune, Maharashtra}
  \resumeSubHeadingListEnd

%-------------EXPERIENCE-----------
\section{EXPERIENCE}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\href{https://hosteze.in}{\textbf{\large{\underline{Developer Intern at Hosteze}}}}}{Aug 2024 - Sep 2024}\\
          \resumeItemListStart
         \resumeItem{\normalsize{Implemented a "Contact via WhatsApp" feature, enabling users to initiate seamless communication directly from the platform. This integration boosted engagement and facilitated direct user interactions.}}
         \resumeItem{\normalsize{Implemented advanced loading skeletons to enhance perceived loading times, delivering a smoother and more responsive user experience.}}
         \resumeItem{\normalsize{Technology Stack: Leveraged ReactJS, NextJS, TypeScript, and Tailwind CSS to optimize frontend performance, build reusable components, and improve code maintainability.}}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://ioittenet.com}{\textbf{\large{\underline{Developer at ACM Web Team}}}}}{Jul 2024 - Present}\\
          \resumeItemListStart
        \resumeItem{\normalsize{Contributed to the development and optimization of websites for the ACM Web Team, supporting various college initiatives.}}
        \resumeItem{\normalsize{Developed websites for IOIT TENET (\href{https://ioittenet.com}{ioittenet.com}) and IOIT MUN (\href{https://ioitmun.com}{ioitmun.com}).}}
        \resumeItem{\normalsize{Worked collaboratively with a team of developers to deliver high-quality web solutions.}}
        \resumeItem{\normalsize{Refactored existing codebases to improve scalability and maintainability.}}
        \resumeItem{\normalsize{Technology Stack: Next.js, ReactJS, TypeScript, GSAP, Three.js.}}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}

    \resumeSubHeadingListStart

    \resumeProjectHeading
      {\href{https://code-complexity-analyzer.vercel.app}{\textbf{\large{\underline{Code Complexity Analyzer}}}} \href{https://github.com/swarooppatilx/code-analyzer}{\raisebox{-0.2\height}\faGithub} \href{https://code-complexity-analyzer.vercel.app}{\raisebox{-0.2\height}\faLink}}{Oct 2024 – Oct 2024}
      \resumeItemListStart
       \resumeItem{\normalsize{Developed a web-based application to help developers analyze the complexity of their code, providing insights into both time and space complexity.}}
       \resumeItem{\normalsize{Used Flask for the backend, Chart.js for data visualization, and Tailwind CSS for styling.}}
       \resumeItem{\normalsize{Implemented code complexity metrics to calculate cyclomatic complexity, maintainability index, and other relevant metrics.}}
       \resumeItem{\normalsize{Skills: Generative AI, Google Gemini, Flask, Tailwind CSS, Chart.js, Prism.js.}}
      \resumeItemListEnd

    \resumeProjectHeading
      {\href{https://scruter.vercel.app}{\textbf{\large{\underline{Scruter}}}} \href{https://github.com/swarooppatilx/scruter}{\raisebox{-0.2\height}\faGithub} \href{https://scruter.vercel.app}{\raisebox{-0.2\height}\faLink}}{Jul 2024 – Aug 2024}
      \resumeItemListStart
      \resumeItem{\normalsize{Scruter is a local classifieds and community site designed to bring people together for buying, selling, and exchanging goods and services.}}
      \resumeItem{\normalsize{Developed features like user authentication, posting listings, and search functionalities.}}
      \resumeItem{\normalsize{Skills: Bootstrap, JavaScript, Application Development, Express.js, Node.js, Progressive Web Applications (PWAs), REST APIs.}}
      \resumeItemListEnd


      \resumeProjectHeading
        {\href{https://health-link-v1.vercel.app}{\textbf{\large{\underline{Health Link}}}} \href{https://github.com/swarooppatilx/health-link}{\raisebox{-0.2\height}\faGithub} \href{https://health-link-v1.vercel.app/}{\raisebox{-0.2\height}\faLink}}{Oct 2024 – Present}
        \resumeItemListStart
        \resumeItem{\normalsize{Developed a comprehensive healthcare app for appointment scheduling, managing medical records, viewing lab results, and booking vaccinations.}}
        \resumeItem{\normalsize{Implemented user authentication, secure data storage, and real-time notifications.}}
        \resumeItem{\normalsize{Skills: Next.js, TypeScript, MongoDB, ReactJS, Shadcn, Tailwind CSS, Progressive Web Applications (PWAs), REST APIs.}}
        \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------ACHIEVEMENTS-----------
\section{ACHIEVEMENTS}
    \resumeSubHeadingListStart
      \resumeItem{\normalsize{Won consolation prize at Navdhara Project Competition for Scruter, Organized by PCCOER, Pune.}}
      \resumeItem{\normalsize{Won 40th place in Top 50 Project Admins at GirlScript Summer of Code 2024 Extended.}}
    \resumeSubHeadingListEnd


\end{document}
